%!TEX root = ../TAMUTemplate.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2016.
%
%  Author: Sean Zachary Roberson
%	 Version 3.16.09
%  Last updated 9/12/2016
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.


\indent It's an interesting thing taking stalk of seven years of one's life. To be so grateful to so many people, but be utterly unable to convey the depth of one's gratitude. Nevertheless, that is just how I feel about my time in graduate school.

It has been a true honor to work with my advisor, Professor Ricardo Eusebi. I remember meeting Ricardo at Fermilab when I was an undergraduate summer student, not realizing that this would be a relationship that would enrich my life forever. I have learned an innumerable amount from Ricardo about an ever widening range of topics, from the intricacies of high energy physics, to the navigation of Texas A\&M University regulation, to the benefits of making a solid plan before execution. I am a better student and physicist because of him.

I must also thank the wider TAMU collider physics group for their support and advise. Whether it was a question on physics, career advice, or time on a computing cluster, this group was always there for me. I have spent a significant amount of time at Texas A\&M, so this list is too long to enumerate, but I want each and every one of these people to know that I am forever grateful to them. I am also thankful for our analysis collaborators Professor Chris Neu and Joseph Goodell from the University of Virginia for their invaluable contributions to this analysis. It is a better and more complete analysis because of them. I am also thankful for my fellow physics graduate students. This group of amazing individuals made my time in College Station that much more enjoyable and helped me to grow as a person outside of physics.

Besides my dissertation analysis I have spent many years working for the JetMET/JERC group within CMS. In that time I have worked with countless individuals who should know what a pleasure it was to work alongside them. There are to many names to list here, but there are some which are deserving of explicit recognition: Mikko Voutilainen, Ia Iashvili, Viola Sordini, Hartmut Stadie, Francesco Pandolfi, Salvatore Rappoccio, Philip Harris, Konstantinos Kousouris, and Robert Schoefbeck.

The CMS experiment is a nearly unbelievable undertaking requiring the hard work and dedication of thousands of scientists, engineers, and students. Like everyone else, I owe some portion of my success and results to each and every one of these people. However, I would be remiss if I didn't single out my collaborators and friends from the Fermilab LPC. John Stupak and Ben Kreis, without you I would be a lesser physicist and weaker rock climber than I am today. Kevin Pedro and Lindsay Grey, I can only hope that when I grow up I understand programming languages like you. Nahn Tran, Jim Dolen, and Justin Pilot, thank you for your support on my JEC/JMAR endeavors. Nadja Strobbe, Hansjorge Webber, Scarlet Norber, Joe Prastika, Jamie Antonelli, and Doug Berry, thank you for indulging my never ending and sometimes random questions. I promise they hade a purpose. To everyone else at the LPC, you my everlasting gratitude for your support.

My parents always told me that we collect some relationships from each stage in our lives; that the ones that remain are meant to be. I met Breann Sitarski as undergraduates at UCLA and we remain friends to this day. Each day I am thankful for her friendship and support. And while this may seem like an odd acknowledgment, I know that Breann and I have talked through many analysis challenges and strategies. She is my sounding board.

Finally, I thank my family, whom I love and appreciate more than words can ever describe. My brother Spenser is and always has been my go-to guy. Whether he knows it or not, he is my inspiration and I can only strive to be as engaged and dedicated as he is. My parents Laura and Gregg have supported me throughout this entire graduate process, even when they couldn't understand the title of my dissertation. I am the person I am today...I am here today because of them.

% use A\&M instead of A$\&$M, not use $A\&M$ as well, the last one won't be bold.
%Texas A\&M University


\pagebreak{}